A finite-state morphological transducer for Kyrgyz

### 2011-10-14 dev/paper/paper.tex
bib updates

%FIXME: What sources did Mirlan use?
%FIXME: Should we say something about how I sometimes consulted Tolgonay, or about where my knowledge of Kyrgyz comes from in the first place?
The understanding of Kyrgyz grammar employed to construct the transducer for this project was gained from the Kyrgyz knowledge of two of our authors.  Mirlan Ipasov is a native speaker of Kyrgyz, and Jonathan Washington is a theoretical and descriptive linguist fluent in Kyrgyz and knowledgeable about Turkic languages.  Some grammar sources were consulted, such as \citet{hebertpoppe1963}, , and , but they were largely not relied on due to their approach to Kyrgyz grammar.

@@

\bibliographystyle{fullname}
\bibliography{paper}

>>>>

%FIXME: What sources did Mirlan use?
%FIXME: Should we say something about how I sometimes consulted Tolgonay, or about where my knowledge of Kyrgyz comes from in the first place?
The understanding of Kyrgyz grammar employed to construct the transducer for this project was gained from the Kyrgyz knowledge of two of our authors.  Mirlan Ipasov is a native speaker of Kyrgyz, and Jonathan Washington is a theoretical and descriptive linguist fluent in Kyrgyz and knowledgeable about Turkic languages.  Some grammar sources were consulted, such as \citet{hebertpoppe1963}, \citet{usonalievomuraliev2003}, and \citet{jumakunova2005}, but they were largely not relied on due to their approach to Kyrgyz grammar.

@@

\bibliographystyle{apa}
\bibliography{paper}
